---
title: "Basic storage, access, and manipulation of phylogenetic sequencing data with *MicrobiomeExperiment*"
date: "`r Sys.Date()`"
package: MicrobiomeExperiment
output:
  BiocStyle::html_document:
    fig_height: 7
    fig_width: 10
    toc: yes
    toc_depth: 2
    number_sections: true
vignette: >
  %\VignetteIndexEntry{MicrobiomeExperiment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---
`r library("knitr")`
`r opts_chunk$set(cache=FALSE, fig.width=9, message=FALSE, warning=FALSE)`

# Load *MicrobiomeExperiment*

```{r load-packages, message=FALSE, warning=FALSE}
library("MicrobiomeExperiment")
```

## Example Data

Example data consists mainly of phyloseq [[@McMurdie2013]] datasets converted to 
`SummarizedExperiment`/`TreeSummarizedExperiment` objects.

```{r, eval=FALSE}
data(GlobalPatterns)
data(esophagus)
data(enterotype)
data(soilrep) 
```

## MicrobiomeExperiment Object Summaries

Since `MicrobiomeExperiment` are `TreeSummarizedExperiment` experiment objects,
the summary should look quite familiar.

```{r}
data(GlobalPatterns)
me <- as(GlobalPatterns,"MicrobiomeExperiment")
me
```

# Functions for working microbiome data

## merging and agglomeration based on taxonomic information.

`agglomerateByRank` constructs a `factor` to guide merging from the available
taxonomic information. For more information on merging have a look at the man
page via `?mergeRows`.

```{r}
# print the available taxonomic ranks
colnames(rowData(me))
taxonomyRanks(me)

# agglomerate at the Family taxonomic rank
x1 <- agglomerateByRank(me, rank = "Family")
## How many taxa before/after agglomeration?
nrow(me)
nrow(x1)

# with agglomeration of the tree
x2 <- agglomerateByRank(me, rank = "Family",
                        agglomerateTree = TRUE)
nrow(x2) # same number of rows, but
rowTree(x1) # ... different
rowTree(x2) # ... tree

## Look at enterotype dataset...
data(enterotype)
## print the available taxonomic ranks. Shows only 1 rank available
## not useful for agglomerateByRank
taxonomyRanks(enterotype)
```
