---
title: "Useful functions for working with *MicrobiomeExperiment*"
date: "`r Sys.Date()`"
package: MicrobiomeExperiment
output:
  BiocStyle::html_document:
    fig_height: 7
    fig_width: 10
    toc: yes
    toc_depth: 2
    number_sections: true
vignette: >
  %\VignetteIndexEntry{MicrobiomeExperiment-fun}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
---


```{r}
knitr::opts_chunk$set(cache=FALSE, fig.width=9, message=FALSE, warning=FALSE)
```

# Introduction

This vignette lists a bunch of useful functions for working with 
*MicrobiomeExperiment* objects and their package of origin.

**Since *MicrobiomeExperiment* are *SingleCellExperiment* objects a lot of these functions are general functions for working with count data. Use these functions based on your knowledge/aim and not because everybody else is using them**

## QC

```{r}
funs <- data.frame(name = c("calculateAverage"),
                   package = c("scater"),
                   functions = c("calculate the average across feature"),
                   situation = c("for checking the mean abundance of microbiome features"))
```

```{r}
knitr::kable(
  funs, caption = 'QC functions for working with MicrobiomeExperiment'
)
```

## Aggregation


```{r}
funs <- data.frame(name = c(),
                   package = c(),
                   functions = c(),
                   situation = c())
```

```{r}
knitr::kable(
  funs, caption = 'Aggregation functions for working with MicrobiomeExperiment'
)
```

## Dimension reduction


```{r}
funs <- data.frame(name = c(),
                   package = c(),
                   functions = c(),
                   situation = c())
```

```{r}
knitr::kable(
  funs, caption = 'Functions for dimension reduction on data of a MicrobiomeExperiment'
)
```

## Plotting


```{r}
funs <- data.frame(name = c(),
                   package = c(),
                   functions = c(),
                   situation = c())
```

```{r}
knitr::kable(
  funs, caption = 'Plotting functions for working with MicrobiomeExperiment'
)
```

## Other 

